%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PlushCV - One Page Two Column Resume
% LaTeX Template
% Version 1.0 (11/28/2021)
%
% Author:
% Jacob Rivera 
%
% Adapted from:
% https://github.com/sansquoi/PlushCV
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{plushcv}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Edgar Jacob}{Rivera Rios}{Software Engineer}{
    \contactline{\href{https://jacobrr.me}{jacobrr.me}}
    {\href{https://www.github.com/edjacob25}{edjacob25}}
    {\href{https://www.linkedin.com/in/jacobrr/}{jacobrr}}
    {\href{mailto:jacob@jacobrr.me}{jacob@jacobrr.me}}
    {\href{tel:+527223966979}{7223966979}}
}

% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.70\textwidth}

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     EDUCATION
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \section{Education}

    \subsection{INGENIERÍA EN SISTEMAS COMPUTACIONALES}
    \rundescript{Instituto Tecnológico de Estudios Superiores de
        Monterrey - Toluca} \location{Aug 2012 - Dec 2016}
    High academical performance program \textbullet{} Honorific Excellence Mention \textbullet{} CENEVAL National Award
    \location{ GPA: 95/100 }
    \sectionsep

    \subsection{MAESTRÍA EN CIENCIAS COMPUTACIONALES (M.C.C.S.)}
    \rundescript{Instituto Tecnológico de Estudios Superiores de
        Monterrey - EDOMEX} \location{Aug 2018 - May 2021}
    Coursework done
    \location{ GPA: 96/100 }
    \sectionsep


    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     EXPERIENCE
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \section{Experience}

    \runsubsection{Expedia Group}
    \descript{| Software Engineer}
    \location{April 2023 – Current}
    \vspace{\topsep} % Hacky fix for awkward extra vertical space
    \begin{tightemize}
        \sectionsep
        \item Working in core internal services, creating and maintaining micro-services that underpin the main business. Mainly in Spring, in both Kotlin and Java.
        \item Integration of these core services with AWS, including CI/CD and related test infrastructure. Worked with Github Actions, ElasticSearch, Wiremock, Spinnaker, and related AWS tech such as EC2, Kinesis, DynamoDB, etc.
    \end{tightemize}
    \sectionsep

    \runsubsection{Qualitest Group in service of Google}
    \descript{| Software Developer}
    \location{June 2021 – December 2022}
    \begin{tightemize}
        \sectionsep
        \item Creating and running text experiments for user engagement in Google Search, using HTML, Java and Javascript.
        \item Creation of internal tools, scripts and data flows in Python, using internal APIs and products.
    \end{tightemize}
    \sectionsep

    \runsubsection{Cosmocolor S.A.}
    \descript{| .NET DEVELOPER }
    \location{July 2017 - August 2018}
    \begin{tightemize}
        \sectionsep
        \item Working in C\#, restoring and upgrading an old ASP.NET MVC 4.5 system, using WebServices, while also developing new systems and modules in .NET Core 2.0, Netstandard 2.0 and ASP.NET Core.
        \item Working with C\#, NHibernate and MS SQL Server
    \end{tightemize}
    \sectionsep

    \runsubsection{Yvi Mx}
    \descript{| Software Developer }
    \location{February 2017 - July 2017}
    \begin{tightemize}
        \sectionsep
        \item Design and implementation of the Yvi backend, which includes a REST API, a notification system integrated with Firebase and a runner for jobs.
        \item DB design and administration in Postgresql
        \item .NET Core in Linux, C\# and using both ASP.NET Core and Entity Framework Core
    \end{tightemize}
    \sectionsep

    \runsubsection{La Moderna}
    \descript{| DEVELOPMENT INTERN }
    \location{August 2016 - December 2016}
    \begin{tightemize}
        \sectionsep
        \item Debugging and maintenance of some legacy systems and development of new modules that work with them
        \item .NET systems, C\# and VB.NET used
    \end{tightemize}
    \sectionsep

    % \runsubsection{FEMSA}
    % \descript{| DEVELOPER }
    % \location{September 2014 - December 2014}
    % \begin{tightemize}
    %     \sectionsep
    %     \item Development of a prototype system to provide control of FEMSA’s vehicular park
    %     \item Java technology using servlets and Java Server Pages
    % \end{tightemize}
    % \sectionsep

\end{minipage}
\hfill
\begin{minipage}[t]{0.25\textwidth}

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     SKILLS
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Skills}
    \subsection*{Languages}
    \vspace{\topsep} % Hacky fix for awkward extra vertical space
    \begin{tightemize}
        \sectionsep
        \item Spanish - Native
        \item English - 650/677 TOEFL ITP
    \end{tightemize}

    \subsection{Programming}
    \sectionsep
    \location{Proficient:}
    C\# \textbullet{} Java \textbullet{} Python \textbullet{} Kotlin \\
    \sectionsep
    \location{Experienced:}
    Javascript \textbullet{} CSS \textbullet{} HTML \textbullet{} C \\
    SQL \textbullet{} \LaTeX \\
    \sectionsep
    \location{Familiar:}
    C++ \textbullet{}  Rust \textbullet{} Go \textbullet{} Erlang \\
    \sectionsep
    \sectionsep
    \subsection{Libraries/Frameworks}
    \sectionsep
    ASPNET Core \textbullet{} Pandas \\ Jekyll \textbullet{} Spring \textbullet{} React \\
    \sectionsep
    \sectionsep
    \subsection{Tools/Platforms}
    \sectionsep
    Git \textbullet{} Android \textbullet{} Docker \\ DO | AWS | GCE \textbullet{} Unity3d \\

    \sectionsep

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     Projects
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \section{Projects}

    \runsubsection{Sharemods}
    \descript{| C\#, ASP NET }
    \location{2020}
    A webpage which allows to share modlists for the videogame Rimworld. It uses common formats for the community and gives a simple way to share the mods you are using and their order for others to apply in their own client. \href{https://sharemods.jacobrr.me/}{Link.}
    \sectionsep

    \runsubsection{Whatsapp Analyzer}
    \descript{| Java/Kotlin, Android App}
    \location{2015}
    Android app which gives an insight of each conversation by showing message counts and statistics. It was initially a python script which evolved into an app.
    \sectionsep

\end{minipage}
\end{document}
